Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-08-15 tex/Main Text/manuscript.tex
做好图3

\subsection*{Causes of water utilization regime changes}
Some main drivers caused the changes of water utilization regime.
% 经济总量提升导致资源耗竭的加速。
(1) The expansion of irrigated area and the economic growth of industry and services are key to the
changes in the tendentiousness of water utilization in P1 and P2.
During P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of xx/year, 
and agriculture was the dominant water use (xx \% of the total).
After entering P2, however, while the expansion of irrigated area stalled, 
industry and services gradually took off, which took up more water resources.
% 用水关系的变化
(2) Efficiency of water use sparkly changed during the P3.
Although both industrial services output and irrigated agricultural area resumed expansion in P3, 
both their output per unit and water consumption per unit area experienced significant declines.
As a result, after the P3, the proportions of the different water-using sectors tend to average out 
while the total water consumption remains stable.
% 不断变化的管理模式。
(3) Changing water management practice contributed between different periods.
In P1, most of the reservoirs are built in regions where water use is growing, 
and the trend of growth in storage capacity and growth in water demand remain relatively consistent regionally.
In P2, on the other hand, the number of additional reservoirs decreases significantly. 
Within P3, the number of reservoirs increases significantly again, 
but the growth of storage capacity does not match the growth of water demand.

>>>>

\subsection*{Causes of water utilization regime changes}

\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/causes.pdf}
	\caption{Combination of three dimensions (S: stresses; T: tendentiousness; P: pattern) in different periods. 
	Size of the points denoting values of the IWRU: the mean of the P1 phase is 0.10, while 0.14, 0.19 in P2 and P3.
	The red indicator line in this ternary plot denotes 1:1 contributions between tendentiousness (T) and patterns (P).
	Two key change points (1978, 1994), along with the beginning (1965) and the ending (2013) of research period, are labelled.}
	\label{fig:Causes}
\end{figure}

Some main drivers caused the changes of water utilization regime (Figure\ref{fig:Causes}).
% 经济总量提升导致资源耗竭的加速。
(1) The expansion of irrigated area and the economic growth of industry and services are key to the
changes in the tendentiousness of water utilization in P1 and P2.
During P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of xx/year, 
and agriculture was the dominant water use (xx \% of the total).
After entering P2, however, while the expansion of irrigated area stalled, 
industry and services gradually took off, which took up more water resources.
% 用水关系的变化
(2) Efficiency of water use sparkly changed during the P3.
Although both industrial services output and irrigated agricultural area resumed expansion in P3, 
both their output per unit and water consumption per unit area experienced significant declines.
As a result, after the P3, the proportions of the different water-using sectors tend to average out 
while the total water consumption remains stable.
% 不断变化的管理模式。
(3) Changing water management practice contributed between different periods.
In P1, most of the reservoirs are built in regions where water use is growing, 
and the trend of growth in storage capacity and growth in water demand remain relatively consistent regionally.
In P2, on the other hand, the number of additional reservoirs decreases significantly. 
Within P3, the number of reservoirs increases significantly again, 
but the growth of storage capacity does not match the growth of water demand.
